Self Regulation Ontology Retest Data Report

### 2018-02-17 code/SRO_Report.Rmd
updating report with new dataset

```{r}
tmp %>%
  group_by(task, key) %>%
  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    values=c("grey65", "grey45", "grey25"))+
  scale_color_discrete(guide = FALSE)+
  xlab("")+
  ylab("Percent")

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
summary(lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```

@@

```{r}
#read t1 data
t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))

@@

  calc_dvs = function(x){
    out = x %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
    return(out)
  }

@@

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())

@@

@@

```{r}
summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
```

@@

Do these differ statistically?

The plot does not suggest so but this model is giving a warning and very high t values. How else should I be checking for differences between these distributions?

```{r}
summary(lmer(value~key*overall_difference*raw_fit+(1|dv), tmp))
```

>>>>

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    values=c("grey65", "grey45", "grey25"))+
  scale_color_discrete(guide = FALSE)+
  xlab("")+
  ylab("Percent")

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```

@@

```{r warning=FALSE, message=FALSE}
#read t1 data
t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))

@@

  calc_dvs = function(x){
    out = x %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]))
                # score = sum(correct))
    return(out)
  }

@@

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
# trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))))
for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  # trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  # ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc", "score_icc"), labels = c("Accuracy", "Average RT", "Score"))))+
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_icc"), labels = c("Accuracy", "Average RT"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())

@@

```{r}
rel_df[c(rel_df$dv %in% grep('hierarchical_rule', rel_df$dv, value = TRUE)),]
```

@@

```{r}
tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000) %>%
  ungroup() %>%
  mutate(overall_difference = as.character(overall_difference),
         raw_fit = as.character(raw_fit),
         rt_acc = as.character(rt_acc)) %>%
  arrange(-icc_median)

sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/ddm_rel_table.doc")
```

Comparing overall vs difference: overall has higher reliability than difference.

```{r}
summary(lmerTest::lmer(icc ~ overall_difference + (1|dv) ,tmp))
```

Comparing raw vs ddm in overall estimates: EZ is significantly better than HDDM and comparable to raw estimates.

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "overall")))
```

Comparing raw vs ddm in difference scores: EZ is significantly worse than HDDM and comparable to raw estimates.

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "difference")))
```

@@

Not checking if these differ significantly because this seems to in the weeds for this paper.
